visitation_bias

### 2021-02-05 code/visitation_bias.Rmd
pretty much finalized analysis, almost done ms

# Collated
bias <- full_join(bias_plantsp, bias_ktype) %>%
  full_join(bias_family) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  filter(bb.sp.abund >= 3) %>% # dprime tends to become binary when n is very low; this threshold removes more than half the data points, but almost all those were ones and zeros. These ones and zeros probably don't mean much, and they make the models hard to fit.
  mutate(bb.sp = factor(bb.sp), 
         yday = yday(date),
         elev = elev.mean/10) %>% #  scale this down for convenience
  mutate(yday0 = scale(yday),  # normalized versions of variables
         elev0 = scale(elev),
         bb.sp.abund0 = scale(bb.sp.abund),
         dprime.sp0 = scale(dprime.sp),
         dprime.ktype0 = scale(dprime.ktype),
         dprime.fam0 = scale(dprime.fam)) %>%
  select(site, date, bb.sp, dprime.sp, dprime.sp0, dprime.ktype, 
         dprime.ktype0, dprime.fam, dprime.fam0, elev, elev0, 
         yday, yday0, bb.sp.abund, bb.sp.abund0, bb.sp.prop.abund, total.flower.cover)

bias2 <- full_join(bias_plantsp, bias_ktype) %>%
  full_join(bias_family) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  #filter(bb.sp.abund >= 3) %>% # dprime tends to become binary when n is very low; this threshold removes more than half the data points, but almost all those were ones and zeros. These ones and zeros probably don't mean much, and they make the models hard to fit.
  mutate(bb.sp = factor(bb.sp), 
         yday = yday(date),
         elev = elev.mean/10) %>% #  scale this down for convenience
  mutate(yday0 = scale(yday),  # normalized versions of variables
         elev0 = scale(elev),
         bb.sp.abund0 = scale(bb.sp.abund),
         dprime.sp0 = scale(dprime.sp),
         dprime.ktype0 = scale(dprime.ktype),
         dprime.fam0 = scale(dprime.fam)) %>%
  select(site, date, bb.sp, dprime.sp, dprime.sp0, dprime.ktype, 
         dprime.ktype0, dprime.fam, dprime.fam0, elev, elev0, 
         yday, yday0, bb.sp.abund, bb.sp.abund0, bb.sp.prop.abund, total.flower.cover)

@@

ggplot(bias1, aes(dprime.sp)) +
  geom_histogram()

ggplot(bias2, aes(dprime.sp)) +
  geom_histogram()
```

@@

I've played around with every way I can think of to add elevation as a predictor, but there just isn't an elevation effect to be found, and loo model evaluation always favors a varying site intercept to a fixed elevation effect. I'm removing those models for the time being to clean up my script. I can always run them again if we decide it is important ot show the model selection process for the paper.
```{r}
# Full data
brm_dprime.sp10 <- brm(dprime.sp ~ yday0 + bb.sp.abund0 + (1 | bb.sp) + (1 | site),
                       cores = 4,
                       iter = 2000,
                       family = "zero_one_inflated_beta", # 
                       file = "../output/brm_dprime.sp10",
                       data = bias2)

summary(brm_dprime.sp10)
conditional_effects(brm_dprime.sp10)
prior_summary(brm_dprime.sp10)
parnames(brm_dprime.sp10)
pp_check(brm_dprime.sp10)
bayes_R2(brm_dprime.sp10)
mcmc_plot(brm_dprime.sp10, pars = "^r_bb.sp")
mcmc_plot(brm_dprime.sp10, pars = "^r_site")

@@

summary(brm_dprime.sp00)
conditional_effects(brm_dprime.sp00)
prior_summary(brm_dprime.sp00)
parnames(brm_dprime.sp00)
pp_check(brm_dprime.sp00)
bayes_R2(brm_dprime.sp00)
mcmc_plot(brm_dprime.sp00, pars = "^r_bb.sp")
mcmc_plot(brm_dprime.sp00, pars = "^r_site")
```

#### 1.3.3.1 Plot
```{r}
# Full data with zero- one-inflation
get_variables(brm_dprime.sp10)

@@

# Subsetted data with skew normal 
get_variables(brm_dprime.sp00)

@@

# 2. Explaining bias
## 2.1 Calculate visitation probability per plant speces/ktype/family
```{r}
pvis_ktype <- visit_cover %>%
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover), # proportional flower cover
         prop.visits = visits/sum(visits), # proportional visits
         visits.bin = factor(if_else(visits > 0, 1, 0))) %>% # binary visits
  group_by(site, date, bb.sp) %>%
  mutate(bb.sp.abund = sum(visits)) %>% # abundance of each BB sp. per site-date
  ungroup() %>%
  left_join(fl_traits) %>% # add floral traits
  left_join(bb_traits) %>% # add BB traits
  mutate(k.type.ss = factor(k.type.ss), # recode variables
         pbl.w.class2 = factor(pbl.w.class2),
         visits = as.integer(visits)) %>%
  filter(!k.type.ss %in% c("9", "10")) %>% # Drop ktypes 9 and 10 since both are extremely rare
  left_join(site_data)  %>%
  mutate(prop.flower.cover0 = scale(prop.flower.cover), # normalized predictors
         bb.sp.abund0 = scale(bb.sp.abund),
         elev.mean0 = scale(elev.mean),
         yday = yday(date), # and add yday variable
         yday0 = scale(yday)) %>%
  select(site, elev.mean0, elev.mean, elev.class2, date, yday, yday0, bb.sp, plant.sp, visits, 
         visits.bin, prop.visits, prop.flower.cover, prop.flower.cover0,
         k.type.ss, bb.sp.abund, bb.sp.abund0, pbl.w.class2) 
```

## 2.2 Multi-level models

### 2.2.1 Preliminary visualization
The tons of zeros are due to the lots of plant species that were present at very low abundance and received few or zero visits. This might not be ideal. We could opt for one of our alternative bias measure, like fold change, which all give something like a poisson distribution, but I don't know if this would be an improvement. We could also filter our data to include only plants that were above some threshold of relative abundance, say, 1%.
```{r}
# Visit.prop
ggplot(filter(pvis_ktype, prop.flower.cover >= 0.05), aes(prop.visits)) +
  geom_histogram()

# Visits.bin
ggplot(pvis_ktype, aes(k.type.ss, fill = visits.bin)) +
  geom_bar()

ggplot(pvis_ktype, aes(elev.mean, prop.visits)) +
  geom_point() +
  geom_smooth() +
  facet_grid(bb.sp~k.type.ss)

# Visits.bin filtered
ggplot(filter(pvis_ktype, prop.flower.cover >= 0.05), aes(k.type.ss, fill = visits.bin)) +
  geom_bar()
```

### 2.2.2 brms models
```{r}
# Zero- one-inflated beta regression
brm_pvis01 <- brm(prop.visits ~ prop.flower.cover0 + 
                    (1 | k.type.ss) + 
                    (1 | site) + 
                    (1 | bb.sp),
                  family = "zero_one_inflated_beta",
                  file = "./output/brm_pvis01",
                  chains = 4,
                  cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

# Poisson models of raw visit counts
brm_pvis00 <- brm(visits ~ prop.flower.cover0 + 
                    bb.sp.abund0 + 
                    (1 | k.type.ss) + 
                    (1 | site) + 
                    (1 | bb.sp),
                  #control = list(adapt_delta = 0.99),
                  family = "poisson",
                  file = "../output/brm_pvis00",
                  chains = 4,
                  #cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

summary(brm_pvis00)
prior_summary(brm_pvis00)
parnames(brm_pvis00)
mcmc_plot(brm_pvis00, pars = c("^r_k"))
mcmc_plot(brm_pvis00, pars = c("^r_s"))
mcmc_plot(brm_pvis00, pars = c("^b_"))
mcmc_plot(brm_pvis00)
conditional_effects(brm_pvis00)
pp_check(brm_pvis00)
bayes_R2(brm_pvis00)

# Perhaps I should add the bb.sp varying intercept effect; otherwise, I think I could be accused of pseudo replication.
brm_pvis11 <- brm(visits ~ prop.flower.cover0 + 
                    bb.sp.abund0 + 
                    (1 | k.type.ss:pbl.w.class2) + 
                    (1 | site) +
                    (1 | bb.sp),
                  family = "poisson",
                  file = "../output/brm_pvis11",
                  chains = 4,
                  #cores = 4,
                  iter = 2000,
                  data = pvis_ktype)

summary(brm_pvis11)
prior_summary(brm_pvis11)
parnames(brm_pvis11)
mcmc_plot(brm_pvis11, pars = c("^r_k"))
mcmc_plot(brm_pvis11, pars = c("^r_b"))
mcmc_plot(brm_pvis11, pars = c("^b_"))
mcmc_plot(brm_pvis11)
conditional_effects(brm_pvis11)
pp_check(brm_pvis11)
bayes_R2(brm_pvis11)
```

#### 2.2.2.1 Plot
```{r}
# Note that the intercept is on the log scale, so if you want to transform it back to predicted # visits, you have to exponentiate it. I think.

## Interaction model
brm_pvis11_plotframe <- brm_pvis11 %>%
  spread_draws(b_Intercept, `r_k.type.ss:pbl.w.class2`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.pbl = `r_k.type.ss:pbl.w.class2`) %>%
  mutate(condition_mean = b_Intercept + r_ktype.pbl) %>%
  separate(condition, c("ktype", "pbl.class"), sep = "_", remove = FALSE) %>%
  mutate(pbl.class = case_when(
    pbl.class == "1" ~ "short",
    pbl.class == "2" ~ "med",
    pbl.class == "3" ~ "long")
    ) %>%
  mutate(ktype = case_when(
    ktype == "0" ~ "NA (0)",
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)", "NA (0)")))

# ggplot(brm_pvis11_plotframe, aes(condition_mean, pbl.class, color = pbl.class, fill = pbl.class)) +
#   stat_pointinterval() +
#   #stat_halfeye(alpha = 0.5, interval_alpha = 1, point_alpha = 1, size = 1, .width = 0.95) +
#   facet_grid(ktype ~ .) +
#   theme_light() +
#   labs(color = "Tongue length", x = "Visits (log-scale)") +
#   guides(fill = FALSE) +
#   theme(axis.title.y=element_blank(),
#         axis.text.y=element_blank(),
#         axis.ticks.y=element_blank())

ggplot(brm_pvis11_plotframe, aes(condition_mean, pbl.class, color = pbl.class, fill = pbl.class)) +
  #stat_pointinterval() +
  stat_halfeye(alpha = 0.4, interval_alpha = 1, point_alpha = 1) +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visits (log-scale)") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(file = "../output/brm_pvis11_plot1.png", width = 7, height = 5.5)

# Just ktype model
brm_pvis00_plotframe <- brm_pvis00 %>%
  spread_draws(b_Intercept, r_k.type.ss[condition, term]) %>% # the back ticks are necessary to escape the :
  mutate(condition_mean = b_Intercept + r_k.type.ss) %>%
  mutate(ktype = case_when(
    condition == "0" ~ "NA",
    condition == "1" ~ "Disc",
    condition == "2" ~ "Funnel",
    condition == "3" ~ "Bell",
    condition == "4" ~ "Stalk-disc",
    condition == "5" ~ "Lip",
    condition == "6" ~ "Flag",
    condition == "7" ~ "Head")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc", "Funnel", "Bell", "Stalk-disc",
                                   "Lip", "Flag", "Head", "NA")))

>>>>

# Collated
## Filtered t0 abund >= 3
bias <- full_join(bias_plantsp, bias_ktype) %>%
  full_join(bias_family) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  filter(bb.sp.abund >= 3) %>% # dprime tends to become binary when n is very low; this threshold removes more than half the data points, but almost all those were ones and zeros. These ones and zeros probably don't mean much, and they make the models hard to fit.
  mutate(bb.sp = factor(bb.sp), 
         yday = yday(date),
         elev = elev.mean/10) %>% #  scale this down for convenience
  mutate(yday0 = scale(yday),  # normalized versions of variables
         elev0 = scale(elev),
         bb.sp.abund0 = scale(bb.sp.abund),
         dprime.sp0 = scale(dprime.sp),
         dprime.ktype0 = scale(dprime.ktype),
         dprime.fam0 = scale(dprime.fam)) %>%
  select(site, date, bb.sp, dprime.sp, dprime.sp0, dprime.ktype, 
         dprime.ktype0, dprime.fam, dprime.fam0, elev, elev0, 
         yday, yday0, bb.sp.abund, bb.sp.abund0, bb.sp.prop.abund, total.flower.cover)

## Unfiltered
bias2 <- full_join(bias_plantsp, bias_ktype) %>%
  full_join(bias_family) %>%
  left_join(site_data) %>% # add site data
  left_join(bb_abundance) %>% # add BB abundance data
  left_join(fl_abundance) %>% # add fl abundance
  #filter(bb.sp.abund >= 3) %>% # dprime tends to become binary when n is very low; this threshold removes more than half the data points, but almost all those were ones and zeros. These ones and zeros probably don't mean much, and they make the models hard to fit.
  mutate(bb.sp = factor(bb.sp), 
         yday = yday(date),
         elev = elev.mean/10) %>% #  scale this down for convenience
  mutate(yday0 = scale(yday),  # normalized versions of variables
         elev0 = scale(elev),
         bb.sp.abund0 = scale(bb.sp.abund),
         dprime.sp0 = scale(dprime.sp),
         dprime.ktype0 = scale(dprime.ktype),
         dprime.fam0 = scale(dprime.fam)) %>%
  select(site, date, bb.sp, dprime.sp, dprime.sp0, dprime.ktype, 
         dprime.ktype0, dprime.fam, dprime.fam0, elev, elev0, 
         yday, yday0, bb.sp.abund, bb.sp.abund0, bb.sp.prop.abund, total.flower.cover)

@@

ggplot(bias2, aes(dprime.sp)) +
  geom_histogram()

ggplot(filter(bias2, bb.sp.abund >= 5), aes(dprime.sp)) +
  geom_histogram()

ggplot(filter(bias2, bb.sp.abund >= 10), aes(dprime.sp)) +
  geom_histogram()

ggplot(filter(bias, bb.sp %in% c("pasc", "prat", "wurf", "soro", "psit", "hort", "telu")), aes(elev, dprime.sp)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~bb.sp)
```

@@

I've played around with every way I can think of to add elevation as a predictor, but there just isn't an elevation effect to be found, and loo model evaluation always favors a varying site intercept to a fixed elevation effect. I'm removing those models for the time being to clean up my script. I can always run them again if we decide it is important ot show the model selection process for the paper.

#### Call models
```{r}
# Full data
brm_dprime.sp10 <- brm(dprime.sp ~ yday0 + bb.sp.abund0 + (1 | bb.sp) + (1 | site),
                       cores = 4,
                       iter = 2000,
                       family = "zero_one_inflated_beta", # 
                       file = "../output/brm_dprime.sp10",
                       data = bias2)

@@

# Abundance threshold >= 5
brm_dprime.sp20 <- brm(dprime.sp ~ yday + bb.sp.abund + (1 | bb.sp) + (1 | site),
                       cores = 4,
                       iter = 2000,
                       family = "zero_one_inflated_beta", # 
                       file = "../output/brm_dprime.sp20",
                       data = filter(bias, bb.sp.abund >= 5))

# Abundance threshold >= 10
brm_dprime.sp30 <- brm(dprime.sp ~ yday + bb.sp.abund + (1 | bb.sp) + (1 | site),
                       cores = 4,
                       iter = 2000,
                       family = "zero_one_inflated_beta", # 
                       file = "../output/brm_dprime.sp30",
                       data = filter(bias, bb.sp.abund >= 10))
```

#### 1.3.3.1 Evaluate models
They just explains so little variance... d' is too unstable at low abundance. I just don't think there is much that can be said here. 
```{r}
# Full data
pp_check(brm_dprime.sp10)
bayes_R2(brm_dprime.sp10)

## QQ plot
qres_dprime10 <- bias2 %>%
  add_predicted_draws(brm_dprime.sp10, n = 20) %>%
  summarise(
    quant_residual = mean(.prediction < dprime.sp)
  )

ggplot(qres_dprime10,
         aes(sample = quant_residual)) +
  geom_qq(distribution = stats::qunif) +
  geom_qq_line(distribution = stats::qunif)

## Predicted vs. data
pred_vs_data_dprime10 <- bias2 %>%
  add_predicted_draws(brm_dprime.sp10, n = 20)

ggplot(pred_vs_data_dprime10, aes(.prediction, dprime.sp)) +
  geom_point(alpha = 0.25)

# Abundance >= 3
pp_check(brm_dprime.sp00)
bayes_R2(brm_dprime.sp00)

## QQ plot
qres_dprime00 <- bias %>%
  add_predicted_draws(brm_dprime.sp00, n = 20) %>%
  summarise(
    quant_residual = mean(.prediction < dprime.sp)
  )

ggplot(qres_dprime00,
         aes(sample = quant_residual)) +
  geom_qq(distribution = stats::qunif) +
  geom_qq_line(distribution = stats::qunif)

## Predicted vs. data
pred_vs_data_dprime00 <- bias %>%
  add_predicted_draws(brm_dprime.sp00, n = 20)

ggplot(pred_vs_data_dprime00, aes(.prediction, dprime.sp)) +
  geom_point(alpha = 0.25) +
  geom_smooth(method = "lm")

# Abundance >= 5
pp_check(brm_dprime.sp20)
bayes_R2(brm_dprime.sp20)

## QQ plot
qres_dprime20 <- filter(bias2, bb.sp.abund >= 5) %>%
  add_predicted_draws(brm_dprime.sp20, n = 20) %>%
  summarise(
    quant_residual = mean(.prediction < dprime.sp)
  )

ggplot(qres_dprime20,
         aes(sample = quant_residual)) +
  geom_qq(distribution = stats::qunif) +
  geom_qq_line(distribution = stats::qunif)

## Predicted vs. data
pred_vs_data_dprime20 <-  filter(bias2, bb.sp.abund >= 5) %>%
  add_predicted_draws(brm_dprime.sp20, n = 20)

ggplot(pred_vs_data_dprime20, aes(.prediction, dprime.sp)) +
  geom_point(alpha = 0.25) +
  geom_smooth(method = "lm")

# Abundance >= 10
pp_check(brm_dprime.sp30)
bayes_R2(brm_dprime.sp30)

## QQ plot
qres_dprime30 <- filter(bias2, bb.sp.abund >= 10) %>%
  add_predicted_draws(brm_dprime.sp30, n = 20) %>%
  summarise(
    quant_residual = mean(.prediction < dprime.sp)
  )

ggplot(qres_dprime30,
         aes(sample = quant_residual)) +
  geom_qq(distribution = stats::qunif) +
  geom_qq_line(distribution = stats::qunif)

## Predicted vs. data
pred_vs_data_dprime30 <-  filter(bias2, bb.sp.abund >= 10) %>%
  add_predicted_draws(brm_dprime.sp20, n = 20)

ggplot(pred_vs_data_dprime30, aes(.prediction, dprime.sp)) +
  geom_point(alpha = 0.210) +
  geom_smooth(method = "lm")

#### 1.3.3.2 Preliminary visualization
```{r}
# Full data
conditional_effects(brm_dprime.sp10)
mcmc_plot(brm_dprime.sp10, pars = "^r_bb.sp")
mcmc_plot(brm_dprime.sp10, pars = "^r_site")

# Abundance >= 3
conditional_effects(brm_dprime.sp00)
mcmc_plot(brm_dprime.sp00, pars = "^r_bb.sp")
mcmc_plot(brm_dprime.sp00, pars = "^r_site")
```

#### 1.3.3.4 Final visualization
```{r}
# Full data with zero- one-inflation
get_variables(brm_dprime.sp10)

@@

# Subsetted data 
get_variables(brm_dprime.sp00)

@@

# 2. Explaining bias
## 2.1 Calculate visitation probability per plant morphotype. Instead of keeping the plant species resolved, we will pool visitation by morphotype. The problem with not pooling by morphotype is that more species-rich morphotypes will be penalized simply because their visitation is diluted across more species.
```{r}
prop_visits_ktype <- visit_cover %>%
  group_by(site, date, bb.sp, k.type.ss) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover))%>% # binary visits
  group_by(site, date, bb.sp) %>%
  mutate(prop.visits = visits/sum(visits),
         bb.sp.abund = sum(visits)) %>% # abundance of each BB sp. per site-date
  ungroup() %>%
  left_join(bb_traits) %>% # add BB traits
  mutate(ktype = factor(k.type.ss), # recode variables
         tongue = factor(pbl.w.class2),
         visits = as.integer(visits)) %>% # so we can run a Poisson model
  left_join(site_data) %>% # add site data
  ungroup() %>%
  mutate(yday = yday(date),
         elev.mean0 = scale(elev.mean),
         yday0 = scale(yday),
         prop.flower.cover0 = scale(prop.flower.cover),
         perc.flower.cover = prop.flower.cover*100,
         bb.sp.abund0 = scale(bb.sp.abund)) %>%
  select(site, elev.mean, date, yday, bb.sp, ktype, visits, 
         prop.visits, perc.flower.cover, bb.sp.abund, tongue,
         elev.mean0, yday0, prop.flower.cover0, bb.sp.abund0) %>%
  mutate(visits.bin = if_else(visits > 0, 1, 0))

write_csv(prop_visits_ktype, "../hpc_packets/prop_visits_ktype.csv")

prop_visits_ktype_pooled <- visit_cover %>%
  group_by(site, date, k.type.ss) %>%
  summarize(flower.cover = sum(flower.cover), # get raw flower cover and visits by site*date*bb.sp*plant.sp
            visits = sum(visits)) %>%
  group_by(site, date) %>%
  mutate(prop.flower.cover = flower.cover/sum(flower.cover),
         prop.visits = visits/sum(visits),
         bb.abund = sum(visits),
         visits = as.integer(visits)) %>%
  mutate(ktype = factor(k.type.ss)) %>%
  left_join(site_data) %>% # add site data
  ungroup() %>%
  mutate(yday = yday(date),
         elev.mean0 = scale(elev.mean),
         yday0 = scale(yday),
         perc.flower.cover = prop.flower.cover*100,
         prop.flower.cover0 = scale(prop.flower.cover),
         bb.abund0 = scale(bb.abund)) %>%
  select(site, elev.mean, date, yday, ktype, visits, 
         prop.visits, bb.abund, perc.flower.cover,
         elev.mean0, yday0, prop.flower.cover0, bb.abund0) %>%
  mutate(visits.bin = if_else(visits > 0, 1, 0))

write_csv(prop_visits_ktype_pooled, "../hpc_packets/prop_visits_ktype_pool.csv")

## 2.2 Multi-level models
### I tried fitting proportional visitation with beta regression models, but the models performed really badly, with R2 < 1%. I was depressed for some time. But then I realized that the problem was probably caused by low abundance species, which constitute most of my data.  For low-abundance species, and especially singletons, proportional visitation tends to be 100% for a single ktype and 0% for all others. That's tough to model. But using the raw count data, that's not a problem, because we could accurately predict that the visitation of a rare species would be extremely low, and the difference between 1 visit and 0 visits is small. So, I am opting for negbinomial models (these are more robust than Poisson, allowing for overdispersion I think --- loo likes them better than Poisson anyway). The costs are (1) I now have to condition on the interaction of BB abundance and proportional floral abundance and (2) it's theoretically possible to predict more visits than bumble bees. As long as the models converge, I don't think that (1) is a problem. (2) is undesirable, but I don't think it's really that serious, since the point is get our predictions close to reality, even if the actual predictions are impossible. I would rather get an impossible prediction that is close to reality than a possible one that is far from it (say, a prediction of 0% when reality is 100% --- no wonder my beta models flopped!). With the negbinomial models, I'm explaining ~50% of the variance, and I call that a win.

If these models are legit --- and I need to be patient in making sure of that --- then I have a jackpot of inference here. I have the morphotype:bb.sp and morphotype:tongue effects in spades. But a really cool and unexpected finding is that there is a decoupling of the intercept and slope terms. Some morphotypes have high intercepts but low slopes, indicating that they are visited heavily even when they are at relatively low abundance. Others have lower intercepts but response more steeply to prop flower cover. I think I can tell a story about that. Finally, there is substantial site variation, which could be interpreted as lability of bias.

But these models need to be scrutinized. In particular, I don't really understand the pp.check output. The negbinomial models seem like they might be weirder than the Poisson models. I could always try zero-inflated models if that seems necessary.
### 2.2.1 Call models
```{r}
## Exploring the differential bias of bumble bee species and tongue length classes towards floral morphotypes
### Bernoulli with binarized visitation
brm_pvis30 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 + perc.flower.cover | ktype:site), # a random intercept and slope for ktype:site
                  family = "bernoulli", 
                  #file = "../output/brm_prop_visits_ktype_10",  # for running locally
                  file = "brm_prop_visits_ktype_30", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))

### Negbinomial 
brm_pvis10 <- brm(as.integer(visits) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 + perc.flower.cover | ktype:site), # a random intercept and slope for ktype:site
                  family = "negbinomial", 
                  #file = "../output/brm_prop_visits_ktype_10",  # for running locally
                  file = "brm_prop_visits_ktype_10", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))

### Zero-inflated negbinomial
brm_pvis11 <- brm(as.integer(visits) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 + perc.flower.cover | ktype:site), # a random intercept and slope for ktype:site
                  family = "zero_inflated_negbinomial", 
                  #file = "../output/brm_prop_visits_ktype_11",  # for running locally
                  file = "brm_prop_visits_ktype_11", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))

### Poisson
brm_pvis20 <- brm(as.integer(visits) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 + perc.flower.cover | ktype:site), # a random intercept and slope for ktype:site
                  family = "Poisson", # because my proportional data have zeros and ones
                  #file = "../output/brm_prop_visits_ktype_20",  # for running locally
                  file = "brm_prop_visits_ktype_20", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))

### Zero-inflated Poisson
brm_pvis21 <- brm(as.integer(visits) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 + perc.flower.cover | ktype:site), # a random intercept and slope for ktype:site
                  family = "zero_inflated_poisson", # because my proportional data have zeros and ones
                  #file = "../output/brm_prop_visits_ktype_21",  # for running locally
                  file = "brm_prop_visits_ktype_21", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))

brm_pvis22 <- brm(as.integer(visits) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 | ktype:site), # a random intercept and slope for ktype:site
                  family = "zero_inflated_poisson", # because my proportional data have zeros and ones
                  #file = "../output/brm_prop_visits_ktype_22",  # for running locally
                  file = "brm_prop_visits_ktype_22", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("9", "10")))
```
### 2.2.2 Evaluate models
```{r}
# Posterior predictive checks
pp_check(brm_pvis10)
pp_check(brm_pvis11)
pp_check(brm_pvis20)
pp_check(brm_pvis21)

# Predictions vs. data
## Get predictions
brm_pvis10_pred <- predict(brm_pvis10) %>%
  as_tibble()

brm_pvis11_pred <- predict(brm_pvis11) %>%
  as_tibble()

brm_pvis20_pred <- predict(brm_pvis20) %>%
  as_tibble()

brm_pvis21_pred <- predict(brm_pvis21) %>%
  as_tibble()

## Add draws
qres10 <- filter(prop_visits_ktype, !ktype %in% c("9", "10")) %>%
  add_predicted_draws(brm_pvis10, n = 10)

qres11 <- filter(prop_visits_ktype, !ktype %in% c("9", "10")) %>%
  add_predicted_draws(brm_pvis11, n = 10)

qres20 <- filter(prop_visits_ktype, !ktype %in% c("9", "10")) %>%
  add_predicted_draws(brm_pvis20, n = 10)

qres21 <- filter(prop_visits_ktype, !ktype %in% c("9", "10")) %>%
  add_predicted_draws(brm_pvis21, n = 10)

## Plot predictions vs. data
ggplot(qres10, aes(.prediction, visits)) +
  geom_point() +
  geom_smooth()

ggplot(qres11, aes(.prediction, visits)) +
  geom_point() +
  geom_smooth()

ggplot(qres20, aes(.prediction, visits)) +
  geom_point() +
  geom_smooth()

ggplot(qres21, aes(.prediction, visits)) +
  geom_point() +
  geom_smooth()
```

### 2.2.3 Preliminary visualization
```{r}
# Negbinmial
get_variables(brm_pvis10)
conditional_effects(brm_pvis10)
mcmc_plot(brm_pvis10, pars = c("^r_ktype:tongue.*Intercept]$"))
mcmc_plot(brm_pvis10, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis10, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis10, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis10, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis10, pars = c("^r_ktype:site.*perc.flower.cover]$"))

# Zero-inflated negbinomial
get_variables(brm_pvis11)
conditional_effects(brm_pvis11)
mcmc_plot(brm_pvis11, pars = c("^r_ktype:tongue.*Intercept]$"))
mcmc_plot(brm_pvis11, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis11, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis11, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis11, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis11, pars = c("^r_ktype:site.*perc.flower.cover]$"))

# Poisson
get_variables(brm_pvis20)
conditional_effects(brm_pvis20)
mcmc_plot(brm_pvis20, pars = c("^r_ktype:tongue.*Intercept]$"))
mcmc_plot(brm_pvis20, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis20, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis20, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis20, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis20, pars = c("^r_ktype:site.*perc.flower.cover]$"))
